Multi-state modelling with msm: a practical course

### 2021-09-15 docs/msmcourse_src/index.Rmd
Better course intro page

9.30 to 12.30 French time (8.30 to 11.30 UK time)

Balance of lectures and practical exercises

All the course material is available at

@@

Laptop with R and the `msm` package installed

Basic knowledge of R

>>>>

This course gives an introduction to the use of the `msm` R package for fitting and predicting from multi-state models for intermittently observed data, in typical medical applications.

There is a balance of short talks and practical exercises.  In the exercises, you will write your own R code, based on the code demonstrated in the talks, to perform multi-state data analyses and answer applied questions.

All the course material is on this website, at

@@

Laptop with R and the `msm` package installed.

Basic knowledge of R.
